### 2023-08-30 paper/sec-dis-pseudodata.tex
removed comparison with whitepaper's yield
Integrating over the diff-xsec we use, we get a smaller total-xsec. A part of this is due to NLO vs LO

In our calculation we assume the central values of the neutrino
fluxes provided by~\cite{Kling:2021gos} and used
for the FPF simulations in~\cite{Feng:2022inv}.
%
The bin-by-bin integrated event yields in Eq.~(\ref{eq:event_yields}) are
obtained by convoluting the incoming neutrino fluxes, for a given geometric acceptance
of the target detector, with the corresponding neutrino differential cross-sections
Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}).
%
Differential event yields are evaluated using
\begin{equation}
  \label{eq:event_yields_calculation}
   N_{\rm ev}^{(i)} = n_T L_T\int_{Q^{2(i)}_{\rm min}}^{Q^{2(i)}_{\rm max}}\int_{x^{(i)}_{\rm min}}^{x^{(i)}_{\rm max}}\int_{E_{\rm min}^{(i)}}^{E_{\rm max}^{(i)}} \frac{dN_{\nu}(E_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma(x,Q^2,E_{\nu})}{dxdQ^2}\right) {\cal A}(x,Q^2,E_{\nu}) dQ^2 dx dE_{\nu} \, ,
\end{equation}
with $n_T$ is the nucleon density of the target detector material, $L_T$ its
length and ${\cal A}(x,Q^2,E_{\nu})$ is an acceptance factor which takes the form of a
step function and accounts for the experimental acceptance thresholds
in $E_\ell$, $\theta_\ell$, and $E_h$
listed in Table~\ref{tab:FPF_experiments}.
%
The incoming neutrino fluxes, which account for the geometry
and neutrino pseudo-rapidity $\eta_\nu$ coverage of the considered detector,
are encoded in $dN_{\nu}(E_\nu)/dE_{\nu}$.
%
We have verified that the differential event yield calculation
implemented in Eq.~(\ref{eq:event_yields_calculation}), when extrapolated to a single bin
covering the full detector acceptance,
is consistent with the fiducial interaction rates presented in~\cite{Feng:2022inv} once DIS cuts are imposed and detector acceptances are accounted for.

>>>>

In our calculation we assume the central values of the neutrino
fluxes provided by~\cite{Kling:2021gos} and used
for the FPF simulations in~\cite{Feng:2022inv}.
%
The bin-by-bin integrated event yields in Eq.~(\ref{eq:event_yields}) are
obtained by convoluting the incoming neutrino fluxes, for a given geometric acceptance
of the target detector, with the corresponding neutrino differential cross-sections
Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}).
%
Differential event yields are evaluated using
\begin{equation}
  \label{eq:event_yields_calculation}
   N_{\rm ev}^{(i)} = n_T L_T\int_{Q^{2(i)}_{\rm min}}^{Q^{2(i)}_{\rm max}}\int_{x^{(i)}_{\rm min}}^{x^{(i)}_{\rm max}}\int_{E_{\rm min}^{(i)}}^{E_{\rm max}^{(i)}} \frac{dN_{\nu}(E_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma(x,Q^2,E_{\nu})}{dxdQ^2}\right) {\cal A}(x,Q^2,E_{\nu}) dQ^2 dx dE_{\nu} \, ,
\end{equation}
with $n_T$ is the nucleon density of the target detector material, $L_T$ its
length and ${\cal A}(x,Q^2,E_{\nu})$ is an acceptance factor which takes the form of a
step function and accounts for the experimental acceptance thresholds
in $E_\ell$, $\theta_\ell$, and $E_h$
listed in Table~\ref{tab:FPF_experiments}.
%
The incoming neutrino fluxes, which account for the geometry
and neutrino pseudo-rapidity $\eta_\nu$ coverage of the considered detector,
are encoded in $dN_{\nu}(E_\nu)/dE_{\nu}$.
%
%We have verified that the differential event yield calculation
%implemented in Eq.~(\ref{eq:event_yields_calculation}), when extrapolated to a single bin
%covering the full detector acceptance,
%is consistent with the fiducial interaction rates presented in~\cite{Feng:2022inv} once DIS cuts are imposed and detector acceptances are accounted for.
%
